---
title: "importDataAndgetInShape"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
  word_document: default
---

This script loads all the R libraries and imports all data from SVN.
It also converts the data to the correct formats. 
This script is sourced to the other scripts in the project, and thus, it always runs.

```{r setup, include=FALSE}
library(plyr)
library(xlsx)
library(sqldf)
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape2)
library(MASS)
library(manipulate)
library(lubridate)
library(base)
library(stringr)
library(corrplot)
library(Amelia)
is.odd <- function(x) x %% 2 != 0 
library(gsheet)
trim <- function (x) gsub("^\\s+|\\s+$", "", x)
library(splines)
library(car)
library(sandwich)
library(RcmdrMisc)

# Setting the directory for knitr, as the dir is reset after running a code chunk.
require("knitr")
opts_knit$set(root.dir = "C:/Users/BiancaClavio/Documents/SVN/01Projects/dropOut/data")
```


####From QlikView To SVN

Steps to take before importing to RStudio:

* Get data from qlikview (grades, enrolStatus) and from Cristina Draghici the kvote and GymData.
* With clickview data import into GoogleSheets go to bottom: REMOVE::::  Selection Status: Uddannelse: Medialogiand 
* Export/download as CSV and move to SVN 

Note: Grades B-passed, I-failed, EB - not graded (not allowed to sit exam), U - no show but their specific meanings regarding when you can take the re-exam.

<br>

###Importing Data From SVN

Setting the working directory to the SVN folder.
```{r}
SVNData<-if(grepl("BiancaClavio", getwd()))
  {'C:/Users/BiancaClavio/Documents/SVN/01Projects/dropOut/data'}else
  {"~/01Projects/dropOut/data/"}

setwd(SVNData)
```

####Interview Files
Importing the interviews files with Danish encoding (UTF-8).
When you read the data in the names will not be changed (check.names=FALSE).
Lastly, we only keep the first seven columns of the first variable ([,1:7]).
```{r}
dfMed1Q999<-read.csv("Med1Q999.csv",
  header = TRUE, fill=TRUE, sep = ",",fileEncoding = "UTF-8")

dfMed1Interviews<-read.csv("Drop-out interviews - questionnaire.csv",
  header = TRUE, fill=TRUE, sep = ",",fileEncoding = "UTF-8", check.names=FALSE)

dfMed1Q999<-dfMed1Q999[,1:7]
```

####Courses and Study Plan Versions
Importing all courses distributed on different study plan versions.
```{r}
dfECTSstruct<-read.csv("course_SPV.csv",
  header = TRUE, fill=TRUE, sep = ",",fileEncoding = "UTF-8")
```

####Enrolment Status For BSc and MSc
Importing the enrolment status of all bachelor and master students on Medialogy from 2011 to 2017. 
The enrollment date at the education (fradatosn) for each education is converted to a date data type.
*stype* stores the type of education, and it coerces its argument to a factor (i.e. "kandidat" and "bachelor").
```{r}
dfEnrolStatusMsc<-read.csv("MedEnrolMScThroughJul2017.csv",
  header = TRUE, fill=TRUE, sep = ",",fileEncoding = "UTF-8", check.names=FALSE)
dfEnrolStatusMsc$fradatosn<-as.Date(
  as.character(dfEnrolStatusMsc$fradatosn), "%d.%m.%Y")
dfEnrolStatusMsc$stype<-as.factor("kandidat")

dfEnrolStatusBsc<-read.csv("MedEnrolBScThroughJul2017.csv",
  header = TRUE, fill=TRUE, sep = ",",fileEncoding = "UTF-8", check.names=FALSE)
dfEnrolStatusBsc$fradatosn<-as.Date(
  as.character(dfEnrolStatusBsc$fradatosn), "%d.%m.%Y")
dfEnrolStatusBsc$stype<-as.factor("bachelor")
dfEnrolStatusBsc$Studieordningskode<-as.factor(NA)
```

Afterwards, the enrolment status of all bachelor and master students are combined by columns or rows (rbind).
Students dropping out due to a lack of qualifications are removed.
A enrolment id is generate in a regular sequence.
Lastly, all names of the students are removed from the dateset.
```{r}
dfEnrolStatus<-rbind(dfEnrolStatusMsc,dfEnrolStatusBsc)
dfEnrolStatus<-dfEnrolStatus[!(dfEnrolStatus$udmeldsn
  =='Afvist på grund af manglende kvalifikationer'),]
dfEnrolStatus$enrolID<-seq(1:nrow(dfEnrolStatus))
dfEnrolStatus$navn<-NULL
```

The combined enrolment status is converted to a date data type for the enrolment date and the last day at the education.
The variable of start years is stored in another variable and is converted to a number (identical to *double*).
```{r}
dfEnrolStatus$fradatosn<-as.Date(as.character(dfEnrolStatus$fradatosn)
  , "%d.%m.%Y")
dfEnrolStatus$slutdatosn<-as.Date(as.character(dfEnrolStatus$slutdatosn)
  , "%d.%m.%Y")
dfEnrolStatus$yearOfEnrolment <- dfEnrolStatus$startaar
dfEnrolStatus$startaar<-as.numeric(as.character(dfEnrolStatus$startaar))
```

The following calculates if a semester has ended. (**Not sure**)
```{r}
dfEnrolStatus$EndSemester<-ifelse(is.na(dfEnrolStatus$slutdatosn),NA,
  ifelse(as.numeric(format(dfEnrolStatus$fradatosn,'%m')<6),(format(dfEnrolStatus$slutdatosn,'%y')
  - dfEnrolStatus$startaar)*2+ ceiling((as.numeric(format(dfEnrolStatus$slutdatosn,'%m')))/6),
  (format(dfEnrolStatus$slutdatosn,'%y')-dfEnrolStatus$startaar)*2
  + floor((as.numeric(format(dfEnrolStatus$slutdatosn,'%m'))-2)/6)))
```

####Grades From High School and AAU
Importing data of students grades in high school (2011-2016), their GPA when entering university (2011-2016), and their grades at AAU (2011-2017). The activities (i.e. the courses) from the grade dataset are stored in another variable.
```{r}
dfSchoolGrades<-read.csv("kot_medialogi_2011_2016_gymfag.csv",
  header = TRUE, fill=TRUE, sep = ",")
dfKvote<-read.csv("kot_medialogi_2011_2016_kvote.csv",
  header = TRUE, fill=TRUE, sep = ",")
dfAAUGrades<-read.csv("MEDgradesTilAug32017.csv",
  header = TRUE, fill=TRUE, sep = ",",fileEncoding = "UTF-8")

dfAktivitetsKode<-sqldf("select distinct aktiv_kode, aktivitet from dfAAUGrades")
```

Converting the exam evaluation date and the grade registration date to a date data type.
```{r}
dfAAUGrades$bedom_dato<- as.Date(as.character(dfAAUGrades$bedom_dato) , "%d.%m.%Y")
dfAAUGrades$reg_dato<- as.Date(as.character(dfAAUGrades$reg_dato) , "%d.%m.%Y")
```

Matches grades with enrolment data.
```{r}
dfAAUGrades<-merge(dfAAUGrades,dfEnrolStatus[,
  c("studienr","startaar","fradatosn","slutdatosn","statussn","udmeldsn")])

```

It only stores the observations where the education enrolment is before the exam evaluation and the end of the education (or NA).
```{r}
dfAAUGrades<-dfAAUGrades[dfAAUGrades$bedom_dato>=dfAAUGrades$fradatosn &
  (dfAAUGrades$bedom_dato<=dfAAUGrades$slutdatosn|is.na(dfAAUGrades$slutdatosn)),]
```

Checks if a student is Danish or international.
```{r}
dfAAUGrades$isIntl<-ifelse(dfAAUGrades$Land=="Danmark",0,1)
```

Creates a row ID sequence in the dataset.
```{r}
dfAAUGrades$rowID<-seq(1:nrow(dfAAUGrades))
```


Remove double entries from re-enrolments with same *studienr* exists twice in dfEnrolStatus:

* *difftime* calculates the difference in seconds between beginning and end.
* Creates a data frame (*distHelp*) with the minimum exam evaluation date as *MinDistanceDays*.
* Matches the grades and the *distHelp*.
* Only stores the data where *DistFromEnrol* is equal to *MinDistanceDays*.

```{r}
dfAAUGrades$DistFromEnrol<-difftime(dfAAUGrades$bedom_dato, dfAAUGrades$fradatosn, 
  tz, units = "days")

distHelp<-sqldf("select studienr, aktiv_kode, bedom_dato, min(bedom_dato-fradatosn) As MinDistanceDays 
  from dfAAUGrades group by studienr, aktiv_kode, bedom_dato")

dfAAUGrades<-merge(dfAAUGrades,distHelp,all.x = TRUE)
dfAAUGrades$aktivitetText<-as.character(dfAAUGrades$aktivitet)

dfAAUGrades<-dfAAUGrades[dfAAUGrades$DistFromEnrol==dfAAUGrades$MinDistanceDays,]
dfAAUGrades$takenInYear<-as.numeric(format(dfAAUGrades$bedom_dato,'%Y'))
```

Calculates which year a student took a course.
```{r}
dfAAUGrades$takenInSem<-ifelse(as.numeric(format(dfAAUGrades$fradatosn,'%m')<6),
  (dfAAUGrades$takenInYear-dfAAUGrades$startaar)*2+ 
  ceiling((as.numeric(format(dfAAUGrades$bedom_dato,'%m')))/6), 
  (dfAAUGrades$takenInYear-dfAAUGrades$startaar)*2+ 
  floor((as.numeric(format(dfAAUGrades$bedom_dato,'%m'))-2)/6))
```


```{r}
dfAAUGrades$monthSemMod<-floor((as.numeric(format(dfAAUGrades$bedom_dato,'%m'))+1)/6)
#EB-couldn't take exam ('hand in blank'), U - not allowed to go to the exam, I - fail, B - pass
gradesPassedLUVec<-c('02'=1,'4'=1,'7'=1,'10'=1,'12'=1,'00'=0,'-3'=0,'B'=1,'EB'=0,'U'=0,'I'=0)
gradesToNumsVec<-c('02'=2,'4'=4,'7'=7,'10'=10,'12'=12,'00'=0,'-3'=-3,'EB'=-5,'U'=-8,'B'=2,'I'=0)

```



```{r}


jobHoursVector<-c('10+ hours a week'=12,'0-5 hours a week'=2.5,'5-10 hours a week'=7.5,'No'=0)
pensumVector<-c('Need to catch up a little'=-1,'Far behind'=-3,'Following just fine'=0,"I'm way ahead"=2) #### Comment: Why do the students ahead have value 2? 
EduPrioVector<-c('1st priority'=1,'2nd priority'=2)
EducationLevelVector<-c('Upper secondary school'=13,'Lower secondary school'=10,'Vocational education'=14,'Academic degree'=17)

dfMed1Interviews$jobHoursPerWeek<-jobHoursVector[as.character(dfMed1Interviews$'Are you currently/planning on having a student job?')]
dfMed1Interviews$AVSCatchUp<-pensumVector[as.character(dfMed1Interviews$'How are you keeping up with the courses? [AVS]')]
dfMed1Interviews$PVCatchUp<-pensumVector[as.character(dfMed1Interviews$'How are you keeping up with the courses? [PV]')]
dfMed1Interviews$GPROCatchUp<-pensumVector[as.character(dfMed1Interviews$'How are you keeping up with the courses? [GPRO]')]
dfMed1Interviews$MedStudyPrio<-EduPrioVector[as.character(dfMed1Interviews$'How did you prioritize the Medialogy education when you applied?')]
dfMed1Interviews$FatherEduYrs<-EducationLevelVector[as.character(dfMed1Interviews$'What is the background of your parents? [Father]')]
dfMed1Interviews$MotherEduYrs<-EducationLevelVector[as.character(dfMed1Interviews$'What is the background of your parents? [Mother]')]
dfMed1Interviews$ParentsEduMax<-ifelse(dfMed1Interviews$FatherEduYrs>dfMed1Interviews$MotherEduYrs,dfMed1Interviews$FatherEduYrs,dfMed1Interviews$MotherEduYrs)
dfMed1Interviews$ParentsEduAvg<-(dfMed1Interviews$FatherEduYrs+dfMed1Interviews$MotherEduYrs)/2
dfMed1Interviews$MedHappyWith<-dfMed1Interviews$'How happy are you with studying Medialogy?'
dfMed1Interviews$MedBelongHere<-dfMed1Interviews$'What is your sense of belonging to Medialogy?'
dfMed1Interviews$WantMScDeg<-ifelse(dfMed1Interviews$'Do you plan on taking a master degree?'!="",grepl("Yes", dfMed1Interviews$'Do you plan on taking a master degree?', fixed=TRUE),NA) 
dfMed1Interviews$WantMedMScDeg<-ifelse(dfMed1Interviews$'Do you plan on taking a master degree?'!="",grepl("Medialogy", dfMed1Interviews$'Do you plan on taking a master degree?', fixed=TRUE),NA) 
colsdfmInt <- sapply(dfMed1Interviews, is.logical)
dfMed1Interviews[,colsdfmInt] <- lapply(dfMed1Interviews[,colsdfmInt], as.numeric)

#library(Rcmdr)

factorListFromInterviews<-c("studienr", "picOnMoodle","hoursWorkedPerWeek", "jobHoursPerWeek","AVSCatchUp","GPROCatchUp","MedStudyPrio","ParentsEduMax","ParentsEduAvg","MedHappyWith","MedBelongHere", "WantMScDeg","WantMedMScDeg")
dfInterviews<-dfMed1Interviews[,factorListFromInterviews]

CourseAcronymsLUVec<-c('Grundlæggende programmering'='GPRO',
                       'Problembaseret læring i videns'='PV',
                       'Animation og grafisk design'='AGD',
                       'Audio-Visuel Sketching'='AVS',
                       'Fysisk interface design'='PID',
                       'Matematik til multimedie-appli'='MMA',
                       'Programmering af interaktive s'='PFI',
                       'Interaktionsdesign'='ID',
                       'A/V produktion'='AVP',
                       'Avanceret A/V-produktion'='AAVP',
                       'Billedbehandling'='IP',
                       'Computergrafik programmering'='CGP',
                       'Design af brugeroplevelsen for'='UXD',
                       'Design og analyse af eksperime'='DAE',
                       'Embodied Interaction'='EI',
                       'Forskning i Medialogi'='RIM',
                       'Foundations in Medialogy'='FoM',
                       'Foundations in Medialogy (Comp'='FoCG',
                       'Foundations in Medialogy (Inte'='FoI',
                       'Foundations in Medialogy (Spil'='FoG',
                       'Kreativ innovation og entrepre'='Ent',
                       'Kreativ leg - teknologisk udfo'='P0',
                       'Lyd- og musikbehandling'='AMP',
                       'Lydbehandling'='AP',
                       'Mediesociologi og psykologi'='MSP',
                       'Multimodal perception og kogni'='MMPC',
                       'Modellering af fysiske systeme'='MPS',
                       'Multivariat statistik og mønst'='MVSP',
                       'Narrativer i digital kultur'='NDK',
                       'Objektorienteret Software Engi'='OSE',
                       'Perception'='Per',
                       'Proceduremæssig programmering'='PP',
                       'Programmering af komplekse sof'='PCS',
                       'Prototyping og fremstillingste'='PFT',
                       'Realtids interfaces og interak'='RTII',
                       'Rendering af computergrafik'='CGR',
                       'Rendering og animation'='RaA',
                       'Screen Media'='SM'
)



# prep entry grades dfEntryGradesAll -------------------------------------------------------

dfGradesPerson<-sqldf('select studienr, GYMFAG, NIVEAU, avg(KARAKTER) as avgGrade from dfSchoolGrades group by studienr, GYMFAG, NIVEAU')
matGrade<-sqldf('select studienr, NIVEAU as "MAT_Niveau", avgGrade as MATGrade from dfGradesPerson where GYMFAG = "MAT" group by studienr, NIVEAU order by studienr, NIVEAU')
matGrade<-matGrade[ !duplicated(matGrade$studienr), ]

engGrade<-sqldf('select studienr, NIVEAU as "ENG_Niveau", avgGrade as ENGGrade from dfGradesPerson where GYMFAG = "ENG" group by studienr, NIVEAU order by studienr, NIVEAU')
engGrade<-engGrade[ !duplicated(engGrade$studienr), ]
danGrade<-sqldf('select studienr, NIVEAU as "DAN_Niveau", avgGrade as DANGrade from dfGradesPerson where GYMFAG = "DAN" group by studienr, NIVEAU order by studienr, NIVEAU')
danGrade<-danGrade[ !duplicated(danGrade$studienr), ]
dfAllGradesXTab <-merge(merge(matGrade,engGrade,all.x = TRUE,all.y = TRUE),danGrade,all.x = TRUE,all.y = TRUE)
rm("matGrade","engGrade","danGrade")
#now contains all SchoolGrades and Kvote information
dfEntryGradesAll<-merge(dfAllGradesXTab,dfKvote,all.y = TRUE,all.x = TRUE)
dfEntryGradesAll$DANGradeX<-ifelse(is.na(dfEntryGradesAll$DANGrade),dfEntryGradesAll$ENGGrade,dfEntryGradesAll$DANGrade)

# prep AAU grades allHardByStudent---------------------------------------------------------


dfAAUGrades$gradeNum<-gradesToNumsVec[as.character(dfAAUGrades$KARAKTER)]
dfAAUGrades$GPAgrade<-gradesToNumsVec[as.character(dfAAUGrades$KARAKTER)]

dfAAUGrades$isPassed<-gradesPassedLUVec[as.character(dfAAUGrades$KARAKTER)]
dfAAUGrades$aktivitetShort<-CourseAcronymsLUVec[as.character(dfAAUGrades$aktivitet)]
sqldf('select distinct aktivitet, aktiv_kode from dfAAUGrades order by aktivitet')

dfhard1st<-sqldf('select studienr, aktivitetShort, max(isPassed) as `1`  from dfAAUGrades where "forsoeg.nr." = 1 and aktivitetShort 
                 in ("GPRO",  "PID", "MMA","PFI","ID","AVS") group by studienr, aktivitetShort, karakter')
dfhard2nd<-sqldf('select studienr, aktivitetShort, max(isPassed) as `2` from dfAAUGrades where "forsoeg.nr." < 3  and aktivitetShort 
                 in ("GPRO",  "PID", "MMA","PFI","ID","AVS")  group by studienr, aktivitetShort, karakter')
df1stGrades<-sqldf('select studienr, aktivitetShort, gradeNum as `1g` from dfAAUGrades where "forsoeg.nr." = 1  and aktivitetShort 
                   in ("GPRO",  "PID", "MMA","PFI","ID","AVS")  group by studienr, aktivitetShort ')
df2ndGrades<-sqldf('select studienr, aktivitetShort, max(gradeNum) as `2g` from dfAAUGrades where "forsoeg.nr." =2 and aktivitetShort 
                   in ("GPRO",  "PID", "MMA","PFI","ID","AVS")  group by studienr, aktivitetShort ')
dfLastGrades<-sqldf('select studienr, aktivitetShort, gradeNum as Lg, avg(takenInSem) as takenInSem from dfAAUGrades where "Sidste.Fors." = "Ja"  and aktivitetShort in ("GPRO",  "PID", "MMA","PFI","ID","AVS")  group by studienr, aktivitetShort ')

sqldf("select aktivitetShort, avg(takenInSem) from dfLastGrades group by aktivitetshort")
#head(sqldf('select studienr from dfhard2nd where studienr not in (select studienr from dfhard1st)'))

dfhard<-merge(dfhard1st,dfhard2nd,all.y = TRUE,all.x = TRUE)
dfhard<-melt(dfhard,id.vars=c("studienr","aktivitetShort"))
allHardByStudent<-dcast(dfhard,studienr~aktivitetShort+variable,fun.aggregate = sum, fill=NA_real_)

dfGradesByTry<-merge(df1stGrades,df2ndGrades,all.y = TRUE,all.x = TRUE)
dfGradesByTry<-merge(dfGradesByTry,dfLastGrades[, names(dfLastGrades) != "takenInSem"],all.y = TRUE,all.x = TRUE)
dfGradesByTry<-melt(dfGradesByTry,id.vars=c("studienr","aktivitetShort"))
#dfGradesByTry$value<-gradesToNumsVec[as.character(dfGradesByTry$value)]
dfGradesByTry<-dcast(dfGradesByTry,studienr~aktivitetShort+variable,fun.aggregate = sum,fill=NA_real_)

#dfLastGrades<-melt(dfLastGrades,id.vars=c("studienr","aktivitetShort"))


# prep enrol info dfM has Enrol status ---------------------------------------------------------
dfM<-dfEnrolStatus
lookupDropOutsVector=c('afslutte'= 0, 'afbrudt'=1, '~ben'=0,'orlov'=0)
lookupDropOutsiUniVector=c(Afsluttet= 0, Afbrudt=1, Indskrevet=0, 'Afbrudt (School skift)'=0,'Afbrudt(Fak skift)'=0,'Afbrudt (SN skift)'=0)
lookupDropOutsUdMeldsn=c('Afbrudt af institutionen'= 1, 'Afbrudt af den studerende'=1, 'Afbrudt ved studieskift'=1,Indskrevet=0, 'Indskrevet'=0,'Afsluttet'=0)

# MISSING FIELD IN CURRENT FILE dfM$isDropOutButInUni<-lookupDropOutsiUniVector[as.character(dfM$statussn)]
#dfM$isDropOut<-lookupDropOutsVector[as.character(dfM$statussn)]
dfM$isDropOut<-lookupDropOutsUdMeldsn[as.character(dfM$udmeldsn)]

dfM<-merge(dfM,dfEntryGradesAll,by= 'studienr', all.y = TRUE,all.x = TRUE)
dfM$snapShotYear<-2017
dfM$campus<-factor(dfM$Campus,levels=c("Aalborg","Kbh.","Esbjerg"))

dfM<-merge(dfM,allHardByStudent,by="studienr",all.x = TRUE,all.y = TRUE)

dfM<-merge(dfM,dfGradesByTry,by="studienr",all.x = TRUE,all.y = TRUE)
dfM<-merge(dfM,dfAAUGrades[!duplicated(dfAAUGrades$studienr),c("studienr","isIntl")],by="studienr",all.x = TRUE)
#dfM<-merge(dfM,dfInterviews,by="studienr")

#dfAll$aktivitet<-as.factor(dfAll$aktivitet)

dfM$mathGradeBinned<-cut(dfM$MATGrade,breaks=c(-6,-1,1.5,3,5.5,8.5,11,18))
dfM$mathGradeBinHighGran<-cut(dfM$MATGrade,breaks=c(-6,1,3,4,5,6,7,9,11,18),right = FALSE)
dfM$ENGGradeBinned<-cut(dfM$ENGGrade,breaks=c(-6,-1,1.5,3,5.5,8.5,11,18),right = FALSE)


dfM<-dfM[!is.na(dfM$MATGrade),]
dfM$mathLevelABC<-dfM$MAT_Niveau
dfM$mathLevel<-ifelse(dfM$MAT_Niveau %in% c("B","C"),"B","A" )
dfM$NAVN<-NULL
dfM$Campus<-NULL
dfPFI<-dfM[dfM$startaar==2015 & !is.na(dfM$startaar),]

dfAll<-merge(dfMed1Q999,dfEnrolStatus,all.x = TRUE)
dfAll<-merge(dfAll,dfInterviews,by="studienr")

lookupDropOutsVector=c('Afsluttet'= 0, 'Afbrudt'=1, 'Indskrevet'=0, 'Afbrudt (School skift)'=1,'Afbrudt(Fak skift)'=1,'Afbrudt (SN skift)'=1,'Afbrudt af den studerende'=1,'Afbrudt af institutionen'=1)
lookupDropOutsiUniVector=c('Afsluttet'= 0, 'Afbrudt'=1, 'Indskrevet'=0, 'Afbrudt (School skift)'=0,'Afbrudt(Fak skift)'=0,'Afbrudt (SN skift)'=0,'Afbrudt af den studerende'=1,'Afbrudt af institutionen'=1)
dfAll$isDropOutButInUni<-lookupDropOutsiUniVector[as.character(dfAll$udmeldsn)]
dfAll$isDropOut<-lookupDropOutsVector[as.character(dfAll$udmeldsn)]

dfAll$DropOutQ999Combo<-ifelse(dfAll$isDropOut==1|dfAll$P0Q999==1|dfAll$P1Q999==1|dfAll$P2Q999==1,1,0)

#remove side entries without data - need from Christina draghizi = missing 10 data points including
dfAll<-dfAll[!is.na(dfAll$isDropOutButInUni),]
dfAll<-merge(dfM,dfAll,all.y = TRUE)


dfMed2Aal<-merge(dfMed1Q999,dfEnrolStatus,all.x = TRUE)
dfMed2Aal<-merge(dfMed2Aal,dfInterviews,by="studienr",all.x = TRUE)
dfMed2Aal<-merge(dfMed2Aal,dfEntryGradesAll,by="studienr",all.x = TRUE)
dfMed2Aal<-merge(dfMed2Aal,dfGradesByTry,by="studienr",all.x = TRUE)
dfMed2Aal<-merge(dfMed2Aal,allHardByStudent,by="studienr",all.x = TRUE)
dfMed2Aal$isDropOutButInUni<-lookupDropOutsiUniVector[as.character(dfMed2Aal$udmeldsn)]
dfMed2Aal$isDropOut<-lookupDropOutsVector[as.character(dfMed2Aal$udmeldsn)]
dfMed2Aal$DropOutQ999Combo<-ifelse(dfMed2Aal$isDropOut==1|dfMed2Aal$P0Q999==1|dfMed2Aal$P1Q999==1|dfMed2Aal$P2Q999==1,1,0)
dfMed2Aal$interviewTaken<-ifelse(is.na(dfMed2Aal$MedHappyWith),0,1)
dfPredList<-c("interviewTaken","picOnMoodle","MATGrade","MAT_Niveau")
dfPredListAndInterview<-c(dfPredList, factorListFromInterviews)

FirstSemFactorList<-c('isDropOut', "interviewTaken", "DANGradeX","MATGrade","ENGGrade", "picOnMoodle","hoursWorkedPerWeek", "jobHoursPerWeek","AVSCatchUp","GPROCatchUp","MedStudyPrio","ParentsEduMax","ParentsEduAvg","MedHappyWith","MedBelongHere", "WantMScDeg","WantMedMScDeg")

dfMed2AalX<-dfMed2Aal[dfMed2Aal$interviewTaken==1 & !is.na(dfMed2Aal$isDropOut) &!is.na(dfMed2Aal$ENGGrade) &!is.na(dfMed2Aal$MATGrade) & !is.na(dfMed2Aal$DANGradeX) & !is.na(dfMed2Aal$GPROCatchUp) & !is.na(dfMed2Aal$hoursWorkedPerWeek),FirstSemFactorList]

```

