---
title: "aggregationOfInformationBySemesters"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## setup ECTS structure of the studyplans

prepares data: row ID, convert to factor/char/date 
```{r}
dfECTSstruct$CourseSPVID<-seq(1:nrow(dfECTSstruct))
dfECTSstruct$CTdf<-as.factor(dfECTSstruct$CTdf)
dfECTSstruct$aktivitetText<-as.character(dfECTSstruct$aktivitet)
dfECTSstruct$fromDate<-as.Date(dfECTSstruct$fromDate,"%d/%m/%Y")
dfECTSstruct$toDate<-as.Date(dfECTSstruct$toDate,"%d/%m/%Y")
```

selects and merges data
```{r}
ectsSumSPbySemAndCT<-sqldf("select SPV, sem, CTdf, aktivitet, sum(nominalECTS) as nominalECTS from dfECTSstruct 
                           group by SPV, sem, CTdf, aktivitet  order by SPV, courseType, sem ")

semStruct<-sqldf("select distinct SPV, sem from dfECTSstruct")
CTdfs<-sqldf("select distinct CTdf from dfECTSstruct")
semStruct<-merge(semStruct,CTdfs)
```

left join (all rows in x, adding matching columns from y)
```{r}
sem<-join(semStruct,ectsSumSPbySemAndCT,by=c("SPV","sem","CTdf"), type="left")
sem$nominalECTS[is.na(sem$nominalECTS)]<-0
```

alias: semStruct as a, sem as b
```{r}
ectsSumSPbySemAndCT<-sqldf('select a.SPV as SPV, a.sem as sem, a.CTdf as CTdf, 
                           round(sum(b.nominalECTS+0),0) as nominalECTS
                           from semStruct as a, sem as b
                           where a.SPV=b.SPV and 
                           b.sem<=a.sem and 
                           a.CTdf=b.CTdf 
                           group by a.SPV, a.sem , a.CTdf')
```
 
prepares data: simplies strings and factorize
```{r}
ectsSumSPbySemAndCT$CTdf<-gsub("project","Pr",ectsSumSPbySemAndCT$CTdf);
ectsSumSPbySemAndCT$CTdf<-gsub("elective","El",ectsSumSPbySemAndCT$CTdf);
ectsSumSPbySemAndCT$CTdf<-factor(ectsSumSPbySemAndCT$CTdf, levels = c("T", "NT", "El","Pr"))
```

paste string with a seperator in header
```{r}
ectsSumSPbySemAndCT$CTdf<-paste(ectsSumSPbySemAndCT$CTdf, "nom", sep = "_")
```


```{r}
dfAAUGradesWODistEnrol<-dfAAUGrades;
dfAAUGradesWODistEnrol$DistFromEnrol<- NULL
```

alias: dfAAUGradesWODistEnrol as a, dfECTSstruct as b, dfEnrolStatus as c
```{r}
dfAAUMarriedGrades<-sqldf('select distinct b.CTdf as bctdf, b.SPV as SPV, b.gradeType as gradeType, b.courseSPVID, 
                          b.fromDate, c.fradatosn as fradatoSNsemCalc, b.toDate, c.enrolID as enrolID, 
                          a.* from dfAAUGradesWODistEnrol as a, 
                          dfECTSstruct as b, 
                          dfEnrolStatus as c where a.type=c.stype and c.studienr=a.studienr 
                          and a.aktivitetText=b.aktivitetText 
                          and c.fradatosn>= b.fromDate 
                          and c.fradatosn<=b.toDate 
                          and a.bedom_dato>=c.fradatosn 
                          and (a.bedom_dato<= c.slutdatosn or c.slutdatosn is Null)')
```


### TODO: I don't understand the meaning of this variable?? The name sounds like it calculates the semester date, but it doesn't
the date when enrolled into the education (POSIXct represents calendar dates and times)
```{r}
dfAAUMarriedGrades$fradatoSNsemCalc<-as.Date(format(as.POSIXct(as.numeric(dfAAUMarriedGrades$fradatoSNsemCalc*3600*24), 
                                                               origin='1970-01-01') , format="%Y-%m-%d"))
```

Converts PF and 7-point scale grades to numbers (similar variables in the import script have other values for the EB and U grades)
```{r}
gradesToGPANumsVec<-c('02'=2,'4'=4,'7'=7,'10'=10,'12'=12,'00'=0,'-3'=-3,'EB'=-4,'U'=-5)
gradesToGPAPFVec<-c('EB'=-4,'U'=-5,'B'=2,'I'=0)

dfAAUMarriedGrades$GPAgrade<-ifelse(dfAAUMarriedGrades$gradeType=="PF",gradesToGPAPFVec[as.character(dfAAUMarriedGrades$KARAKTER)],
                                    gradesToGPANumsVec[as.character(dfAAUMarriedGrades$KARAKTER)])
dfAAUMarriedGrades$rid<-seq(1:nrow(dfAAUMarriedGrades))
```


### HKTODO the below overwrites the data already prepared in getin shape --- 
### need to check this again most likely this is about people taking exams in master that should be taken in BSc and therefore added as e.g. sem 7
Calculates at which semester they take the exam, e.g. to distinct between exam and reexam.
(exam year - year of current semester) * 2 + ((exam month - 14) - 2) / 7
```{r}
dfAAUMarriedGrades$takenInSem<- (as.numeric(format(dfAAUMarriedGrades$bedom_dato,'%Y'))-
                                   as.numeric(format(dfAAUMarriedGrades$fradatoSNsemCalc,'%Y')))*2+ 
                                   floor((as.numeric(format(dfAAUMarriedGrades$bedom_dato-14,'%m'))-2)/7)
```

Selects the SPV and enrolID where the SVP fromDate is before enrolment date and SVP toDate is after enrolment
```{r}
dfSPVSNR<-sqldf('select distinct b.SPV as SPV, c.enrolID as enrolID from dfECTSstruct as b, dfEnrolStatus as c 
                where b.type=c.stype and c.fradatosn>= b.fromDate and c.fradatosn<=b.toDate ')
```

### Comment: I get errors, and table is long-format.
nominal etcs points for each semester and each SPV
```{r}
ectsSumSPbySPVAndCT<-dcast(ectsSumSPbySemAndCT, SPV~sem+CTdf)
ectsSumSPbySemAndCT<-dcast(ectsSumSPbySemAndCT, SPV+sem~CTdf)
ectsSumSPbySemAndCT[is.na(ectsSumSPbySemAndCT$El_nom),]$El_nom<-0
```

## Creates the summaries of achieved ECTS per semester 
semester, bctdf, ECTSpassed, 
create the structure for all
create semesters and edutypes
```{r}
semesters<-data.frame(seq(1:10));names(semesters)<-c("semester"); eduType<-data.frame(c("bachelor","kandidat"));names(eduType)<-"type"
```

multiply semesters with edutypes
```{r}
semSkeleton<-data.frame(merge(CTdfs,semesters));semSkeleton<-merge(semSkeleton,eduType)
```

used SemEduTYpe multiplication to merge with students Enrolments into Edutypes
```{r}
StudieNRSkeleton<-merge(distinct(dfEnrolStatus[,c("enrolID","stype")]),semSkeleton,by.x =c("stype"),by.y = c("type")  )
```

Attained ECTS in a study activity of type bctdf (i.e. PR, T, NT, EL) for each enrolID
```{r}
ECTSattainedMelted<- merge(dfAAUMarriedGrades[dfAAUMarriedGrades$isPassed>0,
                          c("bctdf", "enrolID","takenInSem", "ECTS")], 
                          StudieNRSkeleton,by.x = c("enrolID","bctdf"),
                          by.y =c("enrolID","CTdf") ,all.y=TRUE)
```

highest possible ETCS in a study activity of type bctdf (i.e. PR, T, NT, EL) for each enrolID
```{r}
maxECTSTakenByCourseBySemester<-sqldf('select bctdf, enrolID, takenInSem, aktivitet, type, max(ECTS) as ECTS 
                                      from dfAAUMarriedGrades group by bctdf, enrolID, takenInSem, aktivitet, type')
```


### error: something could be wrong here?
attempted ECTs in a study activity of type bctdf (i.e. PR, T, NT, EL) for each enrolID
```{r}
ECTSattmptedMelted<- merge(maxECTSTakenByCourseBySemester[,c("bctdf", "enrolID","takenInSem", "ECTS")] , 
                           StudieNRSkeleton,by.x = c("enrolID","bctdf"),by.y =c("enrolID","CTdf") ,all.y=TRUE)
```

Prepares and cleans up of attained and attempted ETCS variables
```{r}
ECTSattainedMelted$what<-"atnBy"
ECTSattmptedMelted$what<-"atpIn"
ECTSattainedMelted[is.na(ECTSattainedMelted$ECTS),]$ECTS<-0
ECTSattmptedMelted[is.na(ECTSattmptedMelted$ECTS),]$ECTS<-0
```

### TODO: ask if this still makes sense?
NAs in takenInSem is replaced with the semester value.
```{r}
ECTSattainedMelted[is.na(ECTSattainedMelted$takenInSem),]$takenInSem<-ECTSattainedMelted[is.na(ECTSattainedMelted$takenInSem),]$semester
ECTSattmptedMelted[is.na(ECTSattmptedMelted$takenInSem),]$takenInSem<-ECTSattmptedMelted[is.na(ECTSattmptedMelted$takenInSem),]$semester
```

keeps the attained entries where takenInSem <= semester,
 and keeps the attempted entries where takenInSem == semester
```{r}
ECTSattainedMelted<-ECTSattainedMelted[ECTSattainedMelted$takenInSem<=ECTSattainedMelted$semester,]
ECTSattmptedMelted<-ECTSattmptedMelted[ECTSattmptedMelted$takenInSem==ECTSattmptedMelted$semester,]
ECTSattmptedMelted$takenInSem<-NULL
ECTSattainedMelted$takenInSem<-NULL
```

combines attained and attempted ECTS and simplifies data
```{r}
ECTSperf<-rbind(ECTSattmptedMelted,ECTSattainedMelted)
ECTSperf$bctdf<-gsub("project","Pr",ECTSperf$bctdf);ECTSperf$bctdf<-gsub("elective","El",ECTSperf$bctdf);
ECTSperf$bctdf<-factor(ECTSperf$bctdf, levels = c("T", "NT", "El","Pr"))
ECTSattainedMelted$bctdf<-gsub("project","Pr",ECTSattainedMelted$bctdf);ECTSattainedMelted$bctdf<-gsub("elective","El",ECTSattainedMelted$bctdf);
ECTSattainedMelted$bctdf<-factor(ECTSattainedMelted$bctdf, levels = c("T", "NT", "El","Pr"))
```

reshapes and merges the data
```{r}
ECTSovw<- dcast(ECTSperf,enrolID~semester+bctdf+what,value.var = "ECTS",sum)
ECTSovw<-merge(ECTSovw,dfSPVSNR,by="enrolID")
```

## Preparing GPAavg data
```{r}
GPAavg<- merge(dfAAUMarriedGrades[,c("bctdf", "enrolID","takenInSem", "GPAgrade")] , 
               StudieNRSkeleton,by.x = c("enrolID","bctdf"),by.y =c("enrolID","CTdf") ,all.y=TRUE)
GPAavg<-GPAavg[order(GPAavg$enrolID, GPAavg$bctdf, GPAavg$semester,GPAavg$takenInSem),]
```

keep data where takenInSem <= semester or NAs
```{r}
GPAavg<-GPAavg[GPAavg$takenInSem<=GPAavg$semester|is.na(GPAavg$takenInSem),]
```

preparing aggregations of GPAavg
```{r}
GPAavgagg<-sqldf("select enrolID, bctdf, semester, avg(GPAgrade) as GPAavg from GPAavg group by enrolID, bctdf, semester")
GPAavgagg$bctdf<-gsub("project","Pr",GPAavgagg$bctdf);GPAavgagg$bctdf<-gsub("elective","El",GPAavgagg$bctdf);
GPAavgagg$bctdf<-paste(GPAavgagg$bctdf,"mGPA",sep = "_")
```

reshapes data
```{r}
GPAavgagg<-dcast(GPAavgagg,enrolID~semester+bctdf,value.var = "GPAavg",sum)
```


### TODO: need to verify we have all the students in ECTSovw 
Merges data
```{r}
ectsAggsAll<-merge(ECTSovw,ectsSumSPbySPVAndCT, by="SPV")
ForSvante<-merge(dfEnrolStatus,ectsAggsAll)
ForSvante<-ForSvante[ForSvante$startaar>2011,]
ForSvante<-merge(ForSvante,GPAavgagg)
```

Test
```{r}
sqldf("select studienr, spv, count(studienr) from ForSvante group by studienr,SPV having count(studienr)>1 order by studienr")
```

Includes high school data (currently not used)
```{r}
dfKvote1<-sqldf('select distinct studienr, priop, UDD_KODE, kvotient, kvote, land, Campus from dfKvote ')
dfM1<-sqldf('select distinct studienr, MAT_Niveau, MATGrade, ENG_Niveau, ENGGrade, DAN_Niveau, DANGrade from dfM ')
KvoteHSGrades<-merge(dfKvote1,dfM1) # need to remove studienr duplicates
ForSvante2<-merge(ForSvante,KvoteHSGrades, by = "studienr")

```

Includes high school data with many variables
```{r}
highSchoolData1<-sqldf('select fullname as navn, gender, ADGGRU, zip, residenceBeforeEnrolment, 
                       ageAtEnrolment from highSchoolData')
highSchoolVariables<-unique(merge(dfKvote1,dfM1, by = "studienr"))
ForSvante3<-merge(highSchoolVariables,ForSvante2)
ForSvante3<-merge(highSchoolData1,ForSvante3,by = c("navn"))
ForSvante3<-ForSvante3[ForSvante3$stype=="bachelor",]
```

Test
```{r}
perc.rank <- function(x) trunc(rank(x))/length(x)
MScstudentsGPAavgs<-sqldf("select type, enrolID, sum(ECTS/5*GPAgrade)/(sum(ECTS)/5) as GPAavg, 
                          sum(ECTS) as ECTS from dfAAUMarriedGrades where GPAgrade is not Null and type='kandidat'  group by type, enrolID having sum(ECTS)>=80")
MScstudentsGPAavgs$rank<-perc.rank(MScstudentsGPAavgs$GPAavg)
```

final check of data (for loop is not working)
```{r}
missingInSPV<-data.frame(unique(dfAAUGradesWODistEnrol[!dfAAUGradesWODistEnrol$aktivitet %in% dfECTSstruct$aktivitet,]$aktivitet ) )
missingInSPV['studentCounts'] <- 0
for (i in 1:nrow(missingInSPV)){
  missingInSPV[i,2] <- count(dfAAUGradesWODistEnrol$aktivitet, missingInSPV[i,1])
}
```


## Anonymizes data
```{r}
ForSvante$studienr<-NULL
ForSvante2$studienr<-NULL
ForSvante3$studienr<-NULL
ForSvante$navn<-NULL
ForSvante2$navn<-NULL
ForSvante3$navn<-NULL
dfAAUMarriedGradeFile <- dfAAUMarriedGrades
dfAAUMarriedGradeFile$navn <- NULL
dfAAUMarriedGradeFile$studienr<-NULL
```

Removes duplicates
```{r}
ForSvante<-ForSvante[!duplicated(ForSvante), ]
ForSvante2<-ForSvante2[!duplicated(ForSvante2), ]
```

Write data frames to csv files
```{r}
write.csv(ForSvante,file = "MedDataBScMSc-MoreRowsFewerColumns.csv") # 1714 rows 167 variables
write.csv(ForSvante2,file = "MedData2.csv") # 1826 rows 145 variables # currently not used
write.csv(ForSvante3,file = "MedDataBSc.csv") # 1007 rows 184 variables 
write.csv(dfAAUMarriedGradeFile,file = "dfAAUMarriedGrades.csv")
```

Test
```{r}
studentCnts<-sqldf("select startaar, stype, count(startaar) from ForSvante2 group by startaar, stype order by stype, startaar")
```

Comment: Error in FUN(X[[i]], ...) : object 'type' not found
```{r}
ECTSovwx <- dcast(ECTSattmptedMelted,type+studienr~semester+bctdf+what,value.var = "ECTS",sum)
```

other aggregate approaches not finished ECTSatt <- ECTSattainedMelted %>%  group_by(Category) %>% 
```{r}
#  summarise(Frequency = sum(Frequency))
#  sqldf("select studienr, type, bctdf, b.semester as bySem, ECTS  from dfAAUMarriedGrades, semSkeleton as b where b.semester>=takenInSem ")
```

### todo: sum up staa by enrolmentID and filter out people coming from elsewhere not qualifying for bachelor based on staa
### check  ectsatt to sort out students we shouldn't have e.g. coming from elsewhere
### add the nominal ECTS for that semester
### people that have more than 90 ECTS, e.g. in projects 20082897
### e.g. 20125436 is missing second sem proj in marriedGradesFrame

### TODO: got errors in the lines below
```{r}
testxovw<-merge(ECTSovw[,c("studienr","type")],ECTSovwx[,c("studienr","type")],all.x=TRUE)
testyovw<-sqldf("select a.studienr, a.type, b.studienr, b.type from ECTSovw as a left outer join ECTSovwx as b using (studienr,type) ")

```

Test
```{r}
sqldf("select studienr, fradatosn,strftime('%m', fradatosn) from dfEnrolStatus where strftime('%m', fradatosn)<>'09'")
sqldf("SELECT strftime('%m','now')")
```

