---
title: "Student dropouts 2017/2018"
output: pdf_document
---

```{r setup, include=FALSE}

library(xlsx)
library(sqldf)
library(plyr)
library(dplyr)
library(reshape2)
library(MASS)
library(manipulate)
library(stringr)
library(CTT)
#library(gsubfn)
library(Hmisc)
library(psych)
library(ggplot2)
library(ggpubr)
library(gtable)
library(cowplot)
library(pander)

# Setting the directory for knitr, as the dir is reset after running a code chunk.
library(knitr)
library(kableExtra)
opts_knit$set(root.dir = "Z:/BNC/PBL development project/Data/analysis_data", sep = "")

homeDir<-Sys.getenv("HOME")
```

Analysis of first year students 2017/2018 at Medialogy. May 2018.

```{r include=FALSE}
dfEduStatus <- read.csv("dropOut/MEA_dropouts_reasons.csv", stringsAsFactors = FALSE) # 55 dropouts or Q999
dfSemesterStart <- read.csv("dropOut/data/bsc.csv", stringsAsFactors = FALSE)
dfSemesterStartMEA <- subset(dfSemesterStart, startaar==2017 & Uddannelse=="Medialogi") # 180 students
dfDropoutsMay2018 <- subset(dfEduStatus, Status != "Q999") # 41 students
dfQ999May2018  <- subset(dfEduStatus, Status == "Q999") # 14 students




```


## 1. Dropouts/Q999

Number of student dropouts
```{r echo=FALSE}
dropoutStats <- data.frame(c("AAL", "CPH", "Total"), 
  c( nrow(subset(dfDropoutsMay2018, Campus=="AAL")), nrow(subset(dfDropoutsMay2018, Campus=="CPH")), nrow(dfDropoutsMay2018)),
  c(nrow(subset(dfQ999May2018, Campus=="AAL")), nrow(subset(dfQ999May2018, Campus=="CPH")), nrow(dfQ999May2018)))

names(dropoutStats) <- c(" ","Dropouts", "Q999")

kable(dropoutStats)
```


## 2. Study verification test 
Average scores from student dropouts in different topics:
```{r echo=FALSE}
dfSSPscoresAAL <- read.csv("SSP/SSPgradesTestAAL 02-10.csv", stringsAsFactors = FALSE,header = TRUE, fill=TRUE, sep = ",", check.names=FALSE, encoding="UTF-8")
dfSSPscoresAAL <- subset(dfSSPscoresAAL, State=="Finished") # 90 students
#dfSSPscoresAAL <- subset(dfSSPscoresAAL[,c(1:2,5:6,11:ncol(dfSSPscoresAAL))], State=="Finished") # 90 students

dfSSPscoresCPH <- read.csv("SSP/SSPgradesTestCPH 02-10.csv", stringsAsFactors = FALSE, header = TRUE, fill=TRUE, sep = ",", check.names=FALSE, encoding="UTF-8")
dfSSPscoresCPH <- subset(dfSSPscoresCPH, State=="Finished") # 100 students
#dfSSPscoresCPH <- subset(dfSSPscoresCPH[,c(1:2,5:6,11:ncol(dfSSPscoresCPH))], State=="Finished") # 100 students

dfSSPscoresCPH["Campus"]<-"CPH"
dfSSPscoresAAL["Campus"]<-"AAL"
dfSSPgrades <- rbind(dfSSPscoresCPH,dfSSPscoresAAL) # 190 students
#nrow(dfSSPscoresBind)




dfSSPanswersCPH<-read.csv("SSP/SSPanswersTestCPH 10-10.csv", stringsAsFactors=FALSE, header = TRUE, fill=TRUE, sep = ",", check.names=FALSE, encoding="UTF-8")
dfSSPanswersAAL<-read.csv("SSP/SSPanswersTestAAL 10-10.csv", stringsAsFactors=FALSE, header = TRUE, fill=TRUE, sep = ",", check.names=FALSE, encoding="UTF-8")

dfSSPanswers <- rbind(dfSSPanswersAAL,dfSSPanswersCPH)

```

```{r echo=FALSE}
# computes grades for Q93, Q95 and Q96 (note: change the question type next year to avoid this conversion)
# Problem Q93, Q95 and Q96 contained strings, so I had to change them manually:
# Q93 (study hours): 0 > x < 29 (0%) ; 30 > x < 34 (30%) ; 35 > x < 40 (60%) ; 41 > x (100%)
dfSSPgrades$Q..93..0.09[findInterval(dfSSPanswers$`Response 93`, c(0,30)) == 1L] <- 0
dfSSPgrades$Q..93..0.09[findInterval(dfSSPanswers$`Response 93`, c(30,35)) == 1L] <- 0.3
dfSSPgrades$Q..93..0.09[findInterval(dfSSPanswers$`Response 93`, c(35,40)) == 1L] <- 0.6
dfSSPgrades$Q..93..0.09[findInterval(dfSSPanswers$`Response 93`, c(40,1000)) == 1L] <- 0.9

# Q95 (related work): 0 = x (0%) ; 1 > x < 4 (30%) ; 5 > x < 9 (60%) ; 10 > x (100%)
dfSSPgrades$Q..95..0.09[findInterval(dfSSPanswers$`Response 95`, c(0,0)) == 1L] <- 0
dfSSPgrades$Q..95..0.09[findInterval(dfSSPanswers$`Response 95`, c(0,4)) == 1L] <- 0.3
dfSSPgrades$Q..95..0.09[findInterval(dfSSPanswers$`Response 95`, c(5,9)) == 1L] <- 0.6
dfSSPgrades$Q..95..0.09[findInterval(dfSSPanswers$`Response 95`, c(10,1000)) == 1L] <- 0.9

# Q95 (unrelated work): 0 = x (100%) ; 1 > x < 4 (60%) ; 5 > x < 9 (30%) ; 10 > x (0%)
dfSSPgrades$Q..96..0.09[findInterval(dfSSPanswers$`Response 96`, c(0,0)) == 1L] <- 0.9
dfSSPgrades$Q..96..0.09[findInterval(dfSSPanswers$`Response 96`, c(0,4)) == 1L] <- 0.6
dfSSPgrades$Q..96..0.09[findInterval(dfSSPanswers$`Response 96`, c(5,9)) == 1L] <- 0.3
dfSSPgrades$Q..96..0.09[findInterval(dfSSPanswers$`Response 96`, c(10,1000)) == 1L] <- 0
```


```{r echo=FALSE, warning=FALSE}
dfSSPgradesStat <- data.frame( lapply(dfSSPgrades[11:121], function(x) as.numeric(as.character(x))) )

avgGrades <- NULL
avgGrades['Understanding of Medialogy'] <- list(rowMeans(dfSSPgradesStat[c(98:106)])) # removed 5
avgGrades['Study and work'] <- list(rowMeans(dfSSPgradesStat[93:97]))
avgGrades['Growth mindset'] <- list(rowMeans(dfSSPgradesStat[62:64]))
avgGrades['Grit'] <- list(rowMeans(dfSSPgradesStat[57:61]))
avgGrades['Study habits'] <- list(rowMeans(dfSSPgradesStat[65:68]))
avgGrades['High school habits'] <- list(rowMeans(dfSSPgradesStat[34:45]))
avgGrades['Social support for studying'] <- list(rowMeans(dfSSPgradesStat[c(2:4,7:8,55:56)])) # removed 4, added 2
avgGrades <- data.frame( lapply(avgGrades, function(x) as.numeric(as.character(x))) )

avgGrades[is.na(avgGrades)] <- 0

# normalizes avg grades
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}
norm.avgGrades <- as.data.frame(lapply(avgGrades, normalize))
norm.avgGrades["Campus"] <- dfSSPgrades$Campus
norm.avgGrades["rowID"] <- seq(1:nrow(norm.avgGrades))
norm.avgGrades["Email"] <- dfSSPgrades$Email.address
#norm.avgGrades["Kode"] <- dfSSPgrades$Email.address
names(dfSSPgrades)[1] <- "Lastname"
norm.avgGrades["navn"] <- paste(dfSSPgrades$`First name`, dfSSPgrades$Lastname)

```


Table with avg. scores in SSP for dropouts:
```{r echo=FALSE}
dfDropoutsSSP <- merge(dfDropoutsMay2018, norm.avgGrades)
write.csv(dfDropoutsSSP,file = "SSP/dfDropoutsSSP.csv")

dfDropoutsSSPAAL <- subset(dfDropoutsSSP, Campus=="AAL")
#colMeans(dfDropoutsSSPAAL[20:26])

dfDropoutsSSPCPH <- subset(dfDropoutsSSP, Campus=="CPH")
#colMeans(dfDropoutsSSPCPH[20:26])

dfQ999SSP <- merge(dfQ999May2018, norm.avgGrades)
#colMeans(dfQ999SSP[,5:11])


SSPscoresAVG <- data.frame( c(colMeans(dfQ999SSP[,5:11])),
                   c(colMeans(dfDropoutsSSP[,5:11])), 
                   c(colMeans(dfDropoutsSSPAAL[5:11])), 
                   c(colMeans(dfDropoutsSSPCPH[5:11])))

names(SSPscoresAVG) <- c("Q999", "AAL/CPH dropouts", "AAL dropouts", "CPH dropouts")
kable(SSPscoresAVG, digits = 2)

```


Dropout students scored low in study and work hours (time commitment), especially in AAL. Avg. scores in SSP for Q999 looks similar to dropout students.



\pagebreak



#### Dropouts' SSP scores superimposed on boxplots of all students


```{r include=FALSE}
norm.avgGradesMelt <- melt(norm.avgGrades, id.vars = c("rowID", "Campus","navn"))
norm.avgGradesMelt$variable <- gsub("\\.", " ", norm.avgGradesMelt$variable)
#norm.avgGradesMelt['highRisk'] <- ifelse(norm.avgGradesMelt$rowID %in% highRiskStudents$rowID, 1, 0)
norm.avgGradesMelt$variable <- factor(norm.avgGradesMelt$variable, levels = c('Understanding of Medialogy', 'Study and work', 
                                                                              'Growth mindset','Grit','Study habits',
                                                                              'High school habits','Social support for studying'),ordered = TRUE)

norm.avgGradesMelt1 <- norm.avgGradesMelt
norm.avgGradesMelt1$variable <- gsub("Social support for studying","Social support for studying",norm.avgGradesMelt1$variable)
norm.avgGradesMelt1$variable <- gsub("Study habits","Study habits at AAU",norm.avgGradesMelt1$variable)
norm.avgGradesMelt1$variable <- gsub("Study and work","Time commitments (study and other)",norm.avgGradesMelt1$variable)

norm.avgGradesMelt1$variable <- factor(norm.avgGradesMelt1$variable,
  levels = c('Understanding of Medialogy', 'Time commitments (study and other)',
  'Growth mindset', 'Grit',
  'Study habits at AAU','High school habits',
  'Social support for studying'),ordered = TRUE)


dropoutStudent <- subset(norm.avgGradesMelt1, norm.avgGrades$navn %in% dfDropoutsMay2018$Navn)

pScore <- ggplot(norm.avgGradesMelt1, aes(x=variable, y=value)) +
  geom_boxplot() + 
  coord_flip() +
  labs(y="Figure 1: Boxplots of student self-ratings in 7 topics.") +
  geom_dotplot(data = dropoutStudent,
               aes(x=variable, y=value, fill = Campus),
               binaxis='y',
               stackdir='center',
               binwidth = 0.02) +
  theme_bw() +
  #facet_grid(Campus ~ .) +
  theme(plot.margin = margin(35, 1, 1, 1), # 20
        axis.title.y=element_blank(),
        #axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        #axis.title.x=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```

Colored campus location in boxplot:

```{r echo=FALSE}
pScore
```

\pagebreak

Categorized dropout reasons:

```{r echo=FALSE}

# dropoutReasons <- data.frame( c("A. Det faglige niveau er for højt", "B. Det faglige  niveau er for lavt", "C. Studieformen",
#                        "D. Skift til anden uddannelse på AAU", "E. Skift til anden uddannelsesinstitution", "Udmeldt pba. Sekretæroplysning"),
#                    c( "F. Flytter til anden by", "G. Helbredsmæssige årsager", "H. Økonomiske årsager", "I. Ønsker en pause", 
#                       "K. Ønsker ikke at svare", "Afbrudt af den studerende"),
#                    c( "Afmeldt af studieservice", "Ikke deltaget i førsteårsprøven","Udmeldt pga. afvist dispensation til førsteårsprøven",
#                       "Manglende studieaktivitet inden for 1 år", "Udmeldt pga. afvist dispensation til flere prøveforsøg", ""))

dropoutReasons <- data.frame( c("Det faglige niveau er for hoejt", "Det faglige  niveau er for lavt", "Studieformen",
                       "Skift til anden uddannelse paa AAU", "Skift til anden uddannelsesinstitution", ""),
                   c( "Flytter til anden by", "Helbredsmaessige aarsager", "Oekonomiske aarsager", "Oensker en pause", 
                      "Oensker ikke at svare", "Afbrudt af den studerende"),
                   c( "Afmeldt af studieservice", "Ikke deltaget i foersteaarsproeven", "Manglende studieaktivitet inden for 1 aar",
                      "Udmeldt pga. afvist dispensation til foersteaarsproeven", "Udmeldt pga. afvist dispensation til flere proeveforsoeg",
                      "Udmeldt pba. Sekretaeroplysning"))
names(dropoutReasons) <- c("Educational reasons (A)", "Personal reasons (B)", "Participation reasons (C)")

pander(dropoutReasons,  split.cells = 30, split.table = Inf)

#kable(dropoutReasons) %>%
#  kable_styling(bootstrap_options = "striped", full_width = F)
```


Colored dropout reasons in boxplot:

```{r echo=FALSE}

dropoutStudent['Kode'] <- NA
dropoutStudent$Kode <- dfDropoutsMay2018$Kode[match(dropoutStudent$navn, dfDropoutsMay2018$Navn)]

pScore2 <- ggplot(norm.avgGradesMelt1, aes(x=variable, y=value)) +
  geom_boxplot() + 
  coord_flip() +
  labs(y="Figure 1: Boxplots of student self-ratings in 7 topics.") +
  geom_dotplot(data = dropoutStudent,
               aes(x=variable, y=value, fill = Kode),
               binaxis='y',
               stackdir='center',
               binwidth = 0.02) +
  theme_bw() +
  #facet_grid(Campus ~ .) +
  theme(plot.margin = margin(35, 1, 1, 1), # 20
        axis.title.y=element_blank(),
        #axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        #axis.title.x=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```


```{r echo=FALSE}
pScore2
```















<!-- ## 3. Self-assessment quizzes (SA) in GPRO -->

<!-- 127 students from AAL were enrolled in GPRO on Moodle. 18 dropout students took SA in GPRO.  -->

<!-- Number of students who took an SA at least once (multiple attempts were allowed): -->
```{r echo=FALSE, warning=FALSE}
# dfGPROgradebook <- read.csv("GPRO/15-02-2018_GPRO-gradebook.csv", stringsAsFactors = FALSE,header = TRUE, fill=TRUE, sep = ",", check.names=FALSE, encoding="UTF-8")
# dfGPROgradebook['navn'] <- paste(dfGPROgradebook$`First name`,dfGPROgradebook$Surname)
# 
# 
# dfGPROgradebookDropouts <- merge(dfDropoutsMay2018, dfGPROgradebook) # 18 students
# dfGPROgradebookDropouts[,10:23] <- sapply(dfGPROgradebookDropouts[,10:23], as.numeric)
# dfGPROgradebook[,7:20] <- sapply(dfGPROgradebook[,7:20], as.numeric)
# 
# dfGPROgradebook <- subset(dfGPROgradebook, !(is.na(dfGPROgradebook$`ID number`))) # 127
# 
# # reorder data
# dfGPROgradebook <- dfGPROgradebook[c(1:14, 19, 15, 17, 16, 18, 20)]
# dfGPROgradebookDropouts <- dfGPROgradebookDropouts[c(1:17, 22, 18, 20, 19, 21, 23:26 )]
```

```{r echo=FALSE}
# dfSAcount <- data.frame( c( sapply(dfGPROgradebook[,7:19], function(y) nrow(dfGPROgradebook) - sum(length(which(is.na(y)))))),
#                          c( sapply(dfGPROgradebookDropouts[,26:38], function(y) nrow(dfGPROgradebookDropouts) - sum(length(which(is.na(y)))))))
# 
# names(dfSAcount) <- c("Students", "Dropouts")
# 
# kable(dfSAcount)
```


```{r echo=FALSE}
# Avg. SA scores for dropouts when ignoring uncompleted quizzes (NA in data):
# colMeans(dfGPROgradebookDropouts[,26:38], na.rm=TRUE)
```




<!-- \pagebreak -->



<!-- Avg. SA scores for each SA when replacing NA's with zeros: -->
<!-- ```{r echo=FALSE} -->
<!-- dfGPROgradebook[is.na(dfGPROgradebook)] <- 0 -->
<!-- dfGPROgradebookDropouts[is.na(dfGPROgradebookDropouts)] <- 0 -->

<!-- dfSAcolMeans <- data.frame( c(colMeans(dfGPROgradebook[,7:19])), -->
<!--                             c(colMeans(dfGPROgradebookDropouts[,26:38]))) -->

<!-- names(dfSAcolMeans) <- c("Students", "Dropouts") -->
<!-- kable(dfSAcolMeans) -->

<!-- ``` -->




<!-- ## 4. Tutoring in GPRO (AAL) -->
<!-- - We invited 52 students to tutoring after the midterm exam.  -->

<!-- - 9 students attended the first session. -->

<!-- - 2 students attended the second session. -->

<!-- - 8 of the invited Medialogy students dropped out, only 1 dropout student attended the first tutoring session. -->


<!-- ```{r echo=FALSE} -->
<!-- dfTutoring <- read.csv("GPRO/tutoring.csv", stringsAsFactors = FALSE) # 52 -->

<!-- dfTutoringDropouts <- subset(dfTutoring, dfTutoring$Email %in% dfGPROgradebookDropouts$`Email address`) -->
<!-- ``` -->







<!-- ## 5. Student interviews  -->

<!-- - In December 2017, we conducted interviews with struggling students (based on SSP score and Midterm exam score in GPRO).  -->

<!-- - We invited 10 students from each campus (20 invites in total).  -->

<!-- - AAL conducted single interviews with students, whereas CPH conducted a focus group interview. Not all students attended the interviews. -->

<!-- - Total dropouts of the invited students: 6 (4 from AAL, 2 from CPH) -->

<!-- - Total Q999 of the invited students: 3 (2 from AAL, 1 from CPH) -->

<!-- ```{r echo=FALSE} -->
<!-- dfInterviewsDec2017 <- read.csv("highRiskStudents/studentInterviewInviteDec2017.csv", stringsAsFactors = FALSE) # 20 students -->
<!-- dfInterviewsDec2017Dropouts <- subset(dfDropoutsMay2018, dfDropoutsMay2018$navn %in% dfInterviewsDec2017$navn)  -->
<!-- #nrow(dfInterviewsDec2017Dropouts) # 6 -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- #Dropouts of the interviewed students in AAL: -->
<!-- #nrow(subset(dfInterviewsDec2017Dropouts, Ramme_kode=="DMA1617O")) #4 -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- # Dropouts of the interviewed students in CPH: -->
<!-- #nrow(subset(dfInterviewsDec2017Dropouts, Ramme_kode=="DMK1617O")) #2 -->
<!-- ``` -->


<!-- ```{r echo=FALSE} -->
<!-- # Total Q999 of interviewed students: -->
<!-- dfInterviewsDec2017Q999 <- subset(dfQ999May2018, dfQ999May2018$navn %in% dfInterviewsDec2017$navn) #3 -->
<!-- #nrow(dfInterviewsDec2017Q999) -->
<!-- ``` -->









