
```{r setup, include=FALSE}
library(xlsx)
library(sqldf)
library(plyr)
library(dplyr)
library(reshape2)
library(MASS)
library(manipulate)
library(stringr)
library(CTT)
library(Hmisc)
library(psych)
library(ggplot2)
library(ggpubr)
library(gtable)
library(cowplot)

# Setting the directory for knitr, as the dir is reset after running a code chunk.
library(knitr)
library(kableExtra)

opts_knit$set(root.dir = if(grepl("BiancaClavio", getwd())){'C:/Users/BiancaClavio/Documents/SVN/01Projects/GPRO'} else {paste(homeDir,"~/SVN/01Projects/GPRO/", sep = "")})

knitr::opts_chunk$set(fig.height=2.5) 

# homeDir<-Sys.getenv("HOME")

```


 
```{r include=FALSE, warning=FALSE}
personalized_infoGPRO <- read.csv("studentDataGPRO.csv", stringsAsFactors = FALSE)
GPROprogressTable <- read.csv("GPROprogressTable.csv", stringsAsFactors = FALSE)
GPROprogress <- read.csv("GPROprogress.csv", stringsAsFactors = FALSE)

campus <- personalized_infoGPRO$Campus[i]
name <- personalized_infoGPRO$Name[i]
rowID <- personalized_infoGPRO$rowID[i]
MTscore <- subset(GPROprogress$MTscore, GPROprogress$Email.address %in% personalized_infoGPRO$Email[i])
priorExp <- subset(GPROprogress$PriorEXP, GPROprogress$Email.address %in% personalized_infoGPRO$Email[i])

```

---
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[RE,RO]{`r name`}
- \fancyhead[LE,LO]{Medialogy, `r campus`, 2017}
- \fancyfoot[CE,CO]{INTRODUCTION TO PROGRAMMING}
- \fancyfoot[LE,RO]{\thepage}
output:
  pdf_document: default
urlcolor: blue
---


# Midterm Exam - Student Report

This is a report of your acedemic performance in the the midterm exam of the introduction to programming course (GPRO).

The boxplots[^1] show how you compare to a larger sample of first semester Medialogy students from Aalborg and Copenhagen (see Figure 1). 
Specifically, they indicate the average score of all students in five topics, consisting of the midterm term questions (referred to as Q on the y-axis of Figure 1). 
Your score for each topic in the midterm exam is indicated with red dots.
The scores are normalized on a scale from 0 to 1, indicating the lowest and highest possible scores for each topic.
A score above 0.5 means that you received more than half of the point denoted for the particular topic in the test. The percentiles indicate the percentage of students whose scores are equal to or less than yours. 

[^1]: A *boxplot* illustrates the full range of variation (from min to max), the likely range of variation called the interquartile range (IQR) and a typical value (median). The rectangular box denotes the IQR, corresponding to the middle scores of the dataset - ranging from the 25th to the 75th percentile. The line dividing the box into two parts marks the median. The horizontal lines to the left and right of the IQR (whiskers) are 1.5 times as long as the width of the IQR. Outliers are defined as data points outside the whisker ranges and plotted as black dots.


```{r include=FALSE}

avgMidtermGradesMelt$variable <- gsub("CourseIntroduction","Course introduction (Q1-Q2)",avgMidtermGradesMelt$variable)
avgMidtermGradesMelt$variable <- gsub("VariablesDataMaths","Variables and math (Q3-Q13)",avgMidtermGradesMelt$variable)
# avgMidtermGradesMelt$variable <- gsub("Branching","Branching (Q15-Q18, Q22-Q24)",avgMidtermGradesMelt$variable)
# avgMidtermGradesMelt$variable <- gsub("Looping","Looping (Q19)",avgMidtermGradesMelt$variable)
# avgMidtermGradesMelt$variable <- gsub("Functions","Functions (Q20-Q21)",avgMidtermGradesMelt$variable)

avgMidtermGradesMelt$variable <- factor(avgMidtermGradesMelt$variable,
  levels = c('Functions (Q20-Q21)', 'Looping (Q19)',
  'Branching (Q15-Q18, Q22-Q24)','Variables and math (Q3-Q13)',
  'Course introduction (Q1-Q2)'),ordered = TRUE)

student <- subset(avgMidtermGradesMelt, avgMidtermGradesMelt$rowID %in% personalized_infoGPRO$rowID[i])

# avgMidtermGradesMelt$variable <- gsub("\\.", " ", avgMidtermGradesMelt$variable)
# avgMidtermGradesMelt$variable <- factor(avgMidtermGradesMelt$variable,
#   levels = c('If statements', 'Functions', 'Loops',
#   'Nesting','Logical expressions','Mouse and keyboard input',
#   'Math and expressions','Data type','Variables',
#   'General knowledge','Programming rules'),ordered = TRUE)

pScore <- ggplot(avgMidtermGradesMelt, aes(x=variable, y=value)) +
  geom_boxplot() + 
  coord_flip() +
  labs(y="Figure 1: Boxplots of the scores of all students in five topics.") +
  geom_dotplot(data = student,
               aes(x=variable, y=value, fill = "student data"),
               binaxis='y',
               stackdir='center',
               binwidth = 0.05) +
  theme_bw() +
  #facet_grid(Campus ~ .) +
  theme(plot.margin = margin(35, 1, 1, 1),
        axis.title.y=element_blank(),
        #axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        #axis.title.x=element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position="none")

```


```{r include=FALSE, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE} 
studentTable <- melt(subset(personalized_infoGPRO[,-c(1:2, 13:16)], personalized_infoGPRO$rowID %in% personalized_infoGPRO$rowID[i]))
studentTable1<- NULL
studentTable1 <- data.frame(c(studentTable[-c(6:10),-c(1)]), c(studentTable[-c(1:5), ]))
#studentTable1 <- studentTable1[, c(2,3,1)]
names(studentTable1)[1]<-"Your score"
names(studentTable1)[3]<-"Percentile rank"
row.names(studentTable1) <- NULL
#studentTable1$`Your score` <- as.numeric(levels(studentTable1$`Your score`))[studentTable1$`Your score`]
studentTable1 <- studentTable1[,-c(2)]
#studentTable1 <- data.frame( lapply(studentTable1[nrow(studentTable1),], function(x) as.numeric(as.character(x))) )
#studentTable1['MTQ'] <- c('Q1,Q2', 'Q3-Q13', 'Q15-Q18, Q22-Q24', 'Q19', 'Q20, Q21') 


is.num <- sapply(studentTable1, is.numeric)
studentTable1$`Percentile rank` <- as.numeric(as.character(studentTable1$`Percentile rank`))
studentTable1[is.num] <- sapply(studentTable1[is.num], round, 2)
studentTable1$`Percentile rank` <- round(studentTable1$`Percentile rank`, digits = 0)
studentTable1 <- rbind(studentTable1, c(" "))


tabData <- ggtexttable(studentTable1, rows = NULL, theme = ttheme(base_style = "blank", padding = unit(c(2, 6), "mm")))
showAnalysis <- ggarrange(pScore, tabData, ncol = 2, nrow = 1, align = "h", widths = c(3,1.5))
```

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
showAnalysis
```

Table 1 shows the minimum (min), maximum (max), and average (avg) of the midterm exam scores based on prior programming experience (PriorEXP), retrieved from the study verification test (SSP). The descriptive statistics consist of data from Medalogy students in Aalborg and Copenhagen, of which the number of students in each experience level is indicated with N. You reported having `r priorExp` programming skills, and you scored `r MTscore` in the midterm exam. As you may have heard or experienced, hands-on practise is the key to learn and improve your programming skills. Such experience is a reason why the intermediate prgrammers scored higher in the midterm exam in average, but also why some beginners scored higher than the average intermediate and expert programmers. 

**Table 1: The midterm exam scores based on prior programming experience.**

```{r echo=FALSE}
# ggtexttable
kable(GPROprogressTable[,-1], rows = NULL)
```



