---
title: "ECTS weighting"
output: 
  pdf_document:
    fig_caption: yes
tables: true
---

```{r setup, include=FALSE}
# Created by Ninna Vihrs 2018
# Modified by Bianca Clavio Christensen 2018

library(ggplot2)
library(reshape2)
library(ggpmisc)
library(reshape2)
library(plyr)
library(dplyr)
library(xlsx)
#detach("package:RMySQL", unload=TRUE)
library(sqldf)
knitr::opts_chunk$set(warning = FALSE, echo=FALSE)

# Setting the directory for knitr, as the dir is reset after running a code chunk.
# use the fileshare directory 
library(knitr)
library(kableExtra)
opts_knit$set(root.dir = 'Z:/BNC/PBL development project/data/analysis_data/dropOut/data/')
#knitr::opts_chunk$set(fig.height=3.5) 
homeDir<-Sys.getenv("HOME")
```


```{r include=FALSE}

Grades <- read.csv("dfAAUMarriedGrades.csv", encoding="UTF-8", stringsAsFactors=FALSE)
# db changes to map_SPVCmapping: 
# - Perception SPV2010 + bsc to PF
# - Screen media SPV2010 + bsc to scale
# in-progress: changed the dfAAUMarriedGrades.csv in importData - Copy(2) and in-progress with the aggregation script
# hardcoded the db changes here (fast solution)
Grades[Grades$SPV == "BSc2010" & Grades$aktivitet == "Perception" | 
         (Grades$SPV == "BSc" & Grades$aktivitet == "Perception"), ]$gradeType <- "PF" 
# can't do this, missing 7 point-scale grade
#Grades[Grades$SPV == "BSc2010" & Grades$aktivitet == "Screen Media" |
#         (Grades$SPV == "BSc" & Grades$aktivitet == "Screen Media"), ]$gradeType <- "scale" 

GradesBsc <- Grades[Grades$type=='bachelor', ]
GradesMsc <- Grades[Grades$type=='kandidat', ]

beforeGrades <- count(GradesBsc) # 27731
GradesBsc <- GradesBsc[GradesBsc$gradeType =="scale", ] 
GradesBsc <- GradesBsc[GradesBsc$aktivitet != "Screen Media", ]

# subset and take the highest grade
GradesBsc <- sqldf("SELECT enrolID, aktiv_kode, ECTS, bedom_dato, startaar, takenInSem, CourseLocation, isIntl,
                max(gradeNum) as finalGrade FROM GradesBsc WHERE gradeNum > -4 group by enrolID, aktiv_kode, ECTS")

# filters out exams before 2014 using bedom-dato
GradesBsc$bedom_dato = as.Date(as.character(GradesBsc$bedom_dato), "%Y-%m-%d")
GradesBsc <- GradesBsc[as.numeric(format(GradesBsc$bedom_dato,'%Y')) >= 2014 ,]
# Only looking at the first 6 semesters, BC: doesn't matter for study board? 
#GradesBsc <- GradesBsc[GradesBsc$takenInSem<=6,]
#GradesBsc$isProj <- as.numeric(GradesBsc$bctdf=='project')

Fixed <- sqldf('SELECT enrolID, startaar, isIntl, CourseLocation FROM GradesBsc') 
Fixed <- Fixed[!duplicated(Fixed),]
switch <- Fixed$enrolID[duplicated(Fixed$enrolID)]
#seven students seems to have svitched campus. They are removed because otherwise campus can not be compared
GradesBsc <- GradesBsc[!GradesBsc$enrolID%in%switch,]

# removed 10 pass/fail courses (7 from SPV2010 and 3 from SPV2014) + Screen Media
# removed exams with bedom_dato before 2014
# removed 7 students who changed campus
afterGrades <- count(GradesBsc) # 12594
# checks the number of removed entries
beforeGrades - afterGrades # removed 15137 entries from GradesBsc original

# get study board year variable
GradesBsc$snYear <- NA
GradesBsc[as.numeric(format(GradesBsc$bedom_dato,'%Y')) == 2014 & as.numeric(format(GradesBsc$bedom_dato,'%m')) >= 10 |
            as.numeric(format(GradesBsc$bedom_dato,'%Y')) == 2015 & as.numeric(format(GradesBsc$bedom_dato,'%m')) <= 10 , ]$snYear <- "14/15"
GradesBsc[as.numeric(format(GradesBsc$bedom_dato,'%Y')) == 2015 & as.numeric(format(GradesBsc$bedom_dato,'%m')) >= 10 |
            as.numeric(format(GradesBsc$bedom_dato,'%Y')) == 2016 & as.numeric(format(GradesBsc$bedom_dato,'%m')) <= 10 , ]$snYear <- "15/16"
GradesBsc[as.numeric(format(GradesBsc$bedom_dato,'%Y')) == 2016 & as.numeric(format(GradesBsc$bedom_dato,'%m')) >= 10 |
            as.numeric(format(GradesBsc$bedom_dato,'%Y')) == 2017 & as.numeric(format(GradesBsc$bedom_dato,'%m')) <= 10 , ]$snYear <- "16/17"
GradesBsc <- GradesBsc[!is.na(GradesBsc$snYear),]
# checks the sample population
table(GradesBsc$CourseLocation,GradesBsc$takenInSem)
# Note: cohort 2015 and 2016 haven't finished their bachelor when data was collected in August 2017.
table(GradesBsc$CourseLocation,GradesBsc$snYear)
# Note: no students enrolled in Esbjerg after 2014.

GradesBsc$examID <- seq(1:nrow(GradesBsc))
GradesBsc$ECTsWeight <- GradesBsc$ECTS / 5
#GradesBsc$normGradeWeight <- (GradesBsc$ECTS / 60) * GradesBsc$finalGrade 
GradesBsc$gradeWeight <- GradesBsc$ECTS / 5 * GradesBsc$finalGrade

# code snippet used to count number of students
ID <- levels(factor(GradesBsc$enrolID))
Data <- data.frame(ID)
count(Data) # 1093 students in total
Data <- merge(Data,Fixed, by.y='enrolID', by.x='ID')
table(Data$CourseLocation) # number of students on each campus

################################
# hardcoded
# rewrite later
# without weigthing ECTs

SNdata1415 <- subset(GradesBsc,GradesBsc$snYear == '14/15')
SNdata1516 <- subset(GradesBsc,GradesBsc$snYear == '15/16')
SNdata1617 <- subset(GradesBsc,GradesBsc$snYear == '16/17')


SNdata <- data.frame(Campus=c("AAL","AAL","AAL", "ESB","ESB","ESB", "CPH","CPH","CPH"), Year=c("14/15","15/16","16/17","14/15","15/16","16/17","14/15","15/16","16/17") ) 

# average
SNdata$Avg[1] <- mean(subset(SNdata1415, SNdata1415$CourseLocation=='A')$finalGrade)
SNdata$Avg[2] <- mean(subset(SNdata1516, SNdata1516$CourseLocation=='A')$finalGrade)
SNdata$Avg[3] <- mean(subset(SNdata1617, SNdata1617$CourseLocation=='A')$finalGrade)

SNdata$Avg[4] <- mean(subset(SNdata1415, SNdata1415$CourseLocation=='E')$finalGrade)
SNdata$Avg[5] <- mean(subset(SNdata1516, SNdata1516$CourseLocation=='E')$finalGrade)
SNdata$Avg[6] <- mean(subset(SNdata1617, SNdata1617$CourseLocation=='E')$finalGrade)

SNdata$Avg[7] <- mean(subset(SNdata1415, SNdata1415$CourseLocation=='K')$finalGrade)
SNdata$Avg[8] <- mean(subset(SNdata1516, SNdata1516$CourseLocation=='K')$finalGrade)
SNdata$Avg[9] <- mean(subset(SNdata1617, SNdata1617$CourseLocation=='K')$finalGrade)

#Median
SNdata$Median[1] <- median(subset(SNdata1415, SNdata1415$CourseLocation=='A')$finalGrade)
SNdata$Median[2] <- median(subset(SNdata1516, SNdata1516$CourseLocation=='A')$finalGrade)
SNdata$Median[3] <- median(subset(SNdata1617, SNdata1617$CourseLocation=='A')$finalGrade)

SNdata$Median[4] <- median(subset(SNdata1415, SNdata1415$CourseLocation=='E')$finalGrade)
SNdata$Median[5] <- median(subset(SNdata1516, SNdata1516$CourseLocation=='E')$finalGrade)
SNdata$Median[6] <- median(subset(SNdata1617, SNdata1617$CourseLocation=='E')$finalGrade)

SNdata$Median[7] <- median(subset(SNdata1415, SNdata1415$CourseLocation=='K')$finalGrade)
SNdata$Median[8] <- median(subset(SNdata1516, SNdata1516$CourseLocation=='K')$finalGrade)
SNdata$Median[9] <- median(subset(SNdata1617, SNdata1617$CourseLocation=='K')$finalGrade)

# SD
SNdata$SD[1] <- sd(subset(SNdata1415, SNdata1415$CourseLocation=='A')$finalGrade)
SNdata$SD[2] <- sd(subset(SNdata1516, SNdata1516$CourseLocation=='A')$finalGrade)
SNdata$SD[3] <- sd(subset(SNdata1617, SNdata1617$CourseLocation=='A')$finalGrade)

SNdata$SD[4] <- sd(subset(SNdata1415, SNdata1415$CourseLocation=='E')$finalGrade)
SNdata$SD[5] <- sd(subset(SNdata1516, SNdata1516$CourseLocation=='E')$finalGrade)
SNdata$SD[6] <- sd(subset(SNdata1617, SNdata1617$CourseLocation=='E')$finalGrade)

SNdata$SD[7] <- sd(subset(SNdata1415, SNdata1415$CourseLocation=='K')$finalGrade)
SNdata$SD[8] <- sd(subset(SNdata1516, SNdata1516$CourseLocation=='K')$finalGrade)
SNdata$SD[9] <- sd(subset(SNdata1617, SNdata1617$CourseLocation=='K')$finalGrade)

# count students
SNdata$Students[1] <- nrow(data.frame(unique(subset(SNdata1415, SNdata1415$CourseLocation == 'A')$enrolID)))
SNdata$Students[2] <- nrow(data.frame(unique(subset(SNdata1516, SNdata1516$CourseLocation == 'A')$enrolID)))
SNdata$Students[3] <- nrow(data.frame(unique(subset(SNdata1617, SNdata1617$CourseLocation == 'A')$enrolID)))

SNdata$Students[4] <- nrow(data.frame(unique(subset(SNdata1415, SNdata1415$CourseLocation == 'E')$enrolID)))
SNdata$Students[5] <- nrow(data.frame(unique(subset(SNdata1516, SNdata1516$CourseLocation == 'E')$enrolID)))
SNdata$Students[6] <- nrow(data.frame(unique(subset(SNdata1617, SNdata1617$CourseLocation == 'E')$enrolID)))

SNdata$Students[7] <- nrow(data.frame(unique(subset(SNdata1415, SNdata1415$CourseLocation == 'K')$enrolID)))
SNdata$Students[8] <- nrow(data.frame(unique(subset(SNdata1516, SNdata1516$CourseLocation == 'K')$enrolID)))
SNdata$Students[9] <- nrow(data.frame(unique(subset(SNdata1617, SNdata1617$CourseLocation == 'K')$enrolID)))

# count exams/activities
SNdata$Exams[1] <- nrow(subset(SNdata1415, SNdata1415$CourseLocation=='A'))
SNdata$Exams[2] <- nrow(subset(SNdata1516, SNdata1516$CourseLocation=='A'))
SNdata$Exams[3] <- nrow(subset(SNdata1617, SNdata1617$CourseLocation=='A'))

SNdata$Exams[4] <- nrow(subset(SNdata1415, SNdata1415$CourseLocation=='E'))
SNdata$Exams[5] <- nrow(subset(SNdata1516, SNdata1516$CourseLocation=='E'))
SNdata$Exams[6] <- nrow(subset(SNdata1617, SNdata1617$CourseLocation=='E'))

SNdata$Exams[7] <- nrow(subset(SNdata1415, SNdata1415$CourseLocation=='K'))
SNdata$Exams[8] <- nrow(subset(SNdata1516, SNdata1516$CourseLocation=='K'))
SNdata$Exams[9] <- nrow(subset(SNdata1617, SNdata1617$CourseLocation=='K'))

################################
# with weigthing ECTs for each student
# look at the attained ECTS point for that semester

# sum ECTS for enrolID where year is the same
# i <- 1
# for(i in 1:nrow(SNdata1415)){
#   SNdata1415$attainedECTS[i] <- sum(SNdata1415$ECTS[SNdata1415$enrolID[i]==SNdata1415$enrolID])
#   SNdata1415$gradeSum[i] <- sum(SNdata1415$finalGrade[SNdata1415$enrolID[i]==SNdata1415$enrolID])
#   SNdata1415$weightedAvg <- ( SNdata1415$attainedECTS/ SNdata1415$gradeSum)
# }

i <- 1
for(i in 1:nrow(SNdata1415)){
  SNdata1415$attainedECTS[i] <- sum(SNdata1415$ECTS[SNdata1415$enrolID[i]==SNdata1415$enrolID])
  SNdata1415$gradeSum[i] <- sum(SNdata1415$gradeWeight[SNdata1415$enrolID[i]==SNdata1415$enrolID])
  SNdata1415$weightedAvg[i] <- SNdata1415$gradeSum[i]/ sum(SNdata1415$ECTsWeight[SNdata1415$enrolID[i]==SNdata1415$enrolID])
}

i <- 1
for(i in 1:nrow(SNdata1516)){
  SNdata1516$attainedECTS[i] <- sum(SNdata1516$ECTS[SNdata1516$enrolID[i]==SNdata1516$enrolID])
  SNdata1516$gradeSum[i] <- sum(SNdata1516$gradeWeight[SNdata1516$enrolID[i]==SNdata1516$enrolID])
  SNdata1516$weightedAvg[i] <- SNdata1516$gradeSum[i]/ sum(SNdata1516$ECTsWeight[SNdata1516$enrolID[i]==SNdata1516$enrolID])
}

i <- 1
for(i in 1:nrow(SNdata1617)){
  SNdata1617$attainedECTS[i] <- sum(SNdata1617$ECTS[SNdata1617$enrolID[i]==SNdata1617$enrolID])
  SNdata1617$gradeSum[i] <- sum(SNdata1617$gradeWeight[SNdata1617$enrolID[i]==SNdata1617$enrolID])
  SNdata1617$weightedAvg[i] <- SNdata1617$gradeSum[i]/ sum(SNdata1617$ECTsWeight[SNdata1617$enrolID[i]==SNdata1617$enrolID])
}

# remove dublicated enrolID
SNdata1415w <- SNdata1415
SNdata1415w <- SNdata1415w[!duplicated(SNdata1415w[c("enrolID")]),]

SNdata1516w <- SNdata1516
SNdata1516w <- SNdata1516w[!duplicated(SNdata1516w[c("enrolID")]),]

SNdata1617w <- SNdata1617
SNdata1617w <- SNdata1617w[!duplicated(SNdata1617w[c("enrolID")]),]


############################################
# grades weighted based on a student's attained ects in a year

SNdata$wAvg[1] <- mean(subset(SNdata1415w, SNdata1415w$CourseLocation=='A')$weightedAvg)
SNdata$wAvg[2] <- mean(subset(SNdata1516w, SNdata1516w$CourseLocation=='A')$weightedAvg)
SNdata$wAvg[3] <- mean(subset(SNdata1617w, SNdata1617w$CourseLocation=='A')$weightedAvg)

SNdata$wAvg[4] <- mean(subset(SNdata1415w, SNdata1415w$CourseLocation=='E')$weightedAvg)
SNdata$wAvg[5] <- mean(subset(SNdata1516w, SNdata1516w$CourseLocation=='E')$weightedAvg)
SNdata$wAvg[6] <- mean(subset(SNdata1617w, SNdata1617w$CourseLocation=='E')$weightedAvg)

SNdata$wAvg[7] <- mean(subset(SNdata1415w, SNdata1415w$CourseLocation=='K')$weightedAvg)
SNdata$wAvg[8] <- mean(subset(SNdata1516w, SNdata1516w$CourseLocation=='K')$weightedAvg)
SNdata$wAvg[9] <- mean(subset(SNdata1617w, SNdata1617w$CourseLocation=='K')$weightedAvg)

```

The dataset contains Medialogy project and course exams which are graded on the 7-point scale. It includes exams taken in 2014 and after, meaning that the dataset also has entries from students enrolled earlier than 2014, down to 2009. We only use the last attempt that a students received for a particular exam, i.e. their highest grade. Table 1 shows the number of students on each campus and each semester. Note that cohort 2015 and 2016 haven't finished their bachelor when data was collected in August 2017. Moreover, no students enrolled to the Medialogy bachelor at Esbjerg after 2014. Table 2 shows the grade average, weighted average, median, and standard deviations for each campi and each year. The weighted grade average is calculated for each student and weights a grade based on ETCS for an exam (e.g. a 5-ECTS exam grade weights 1, whereas a 15-ECTS exam grade weights 3).

Excluded from the analysis:

- 10 pass/fail course exams
- 7 students who changed campus
- students with merit from other educations
- the students' previous attempt in an exam

```{r}
kable(table(GradesBsc$CourseLocation,GradesBsc$takenInSem), digits = 2, caption = "Number of students on each campus and each semester.") %>%
   kable_styling(latex_options = "hold_position")
```


```{r}
kable(SNdata[c(1:2,6:7,3,8,4:5)], digits = 2, caption = "Number of students, number of exams, grade average (Avg), weighted grade average (wAvg), grade median, and standard deviation of grades (SD) for each campus and each year. The grades are retrieved from the students' last exam in projects or courses. The weighted grade is based on the ECTS of an exam (e.g. a 5-ECTS exam grade weights 1, whereas a 15-ECTS exam grade weights 3), and the weighted average is first calculated for each student in a particular year and then for the campus-year group. The other measures are calculated for the all exam grades.") %>%
   kable_styling(latex_options = "hold_position")
```

```{r}
#kable(SNdata[c(1:2,8:10)], digits = 2, caption = "Grade average, median, and standard deviations for each campi and each year. The grades are weighted based on the total norminated ECTS points in a year.") %>%
#  kable_styling(latex_options = "hold_position")
```

```{r}
# kable(SNdata[c(1:2,11:13)], digits = 2, caption = "Grade average, median, and standard deviations for each campi and each year. The grades are weighted based on a student's total attained ECTS in a year.") %>%
#   kable_styling(latex_options = "hold_position")
```


```{r}
#kable(SNdata[c(1:3,6:8,11)], digits = 2)
```

